---
title: "Simulations"
format: pdf
editor: visual
---

```{r}
set.seed(219)
source("bayesian_ssr.R")
```

## Scenario 1-5

```{r}

alpha<-runif(5000,0,1000)
beta<-alpha
df_sample_size<-tibble()

df_q_andmu_posteriors_50<-tibble()
df_alpha_beta_posteriors_50<-tibble()
df_D_posteriors_50<-tibble()
interim_allocation_50<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()

df_q_andmu_posteriors_125<-tibble()
df_alpha_beta_posteriors_125<-tibble()
df_D_posteriors_125<-tibble()
interim_allocation_125<-tibble()

for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior=c(1,1,1,1),delta_star=0.1)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 1
  length1<-round(aux$treatment1/2)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/2)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/2)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment4/2)
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_50=tibble(treatment_assignment,y)
  aux_post_50<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_50)
  
  df_q_andmu_posteriors_50<-rbind(df_q_andmu_posteriors_50,aux_post_50$q_andmu_posteriors)
  df_alpha_beta_posteriors_50<-rbind(df_alpha_beta_posteriors_50,aux_post_50$alpha_beta_params)
  df_D_posteriors_50<-rbind(df_D_posteriors_50,aux_post_50$D)
  
  treatment_differences_50<-get_treatment_difference(aux_post_50$q_andmu_posteriors,aux_post_50$D,aux_post_50$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_50)
  interim_allocation_50<-rbind(interim_allocation_50,new_r)

  #Scenario 2
  
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment4/4)
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-rbind(df_q_andmu_posteriors_25,aux_post_25$q_andmu_posteriors)
  df_alpha_beta_posteriors_25<-rbind(df_alpha_beta_posteriors_25,aux_post_25$alpha_beta_params)
  df_D_posteriors_25<-rbind(df_D_posteriors_25,aux_post_25$D)
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)

  
  #Scenario 3
  
  length1<-round(aux$treatment1/8)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/8)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/8)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment4/8)
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_125=tibble(treatment_assignment,y)
  
  aux_post_125<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_125)
  
  df_q_andmu_posteriors_125<-rbind(df_q_andmu_posteriors_125,aux_post_125$q_andmu_posteriors)
  df_alpha_beta_posteriors_125<-rbind(df_alpha_beta_posteriors_125,aux_post_125$alpha_beta_params)
  df_D_posteriors_125<-rbind(df_D_posteriors_125,aux_post_125$D)
  
  treatment_differences_125<-get_treatment_difference(aux_post_125$q_andmu_posteriors,aux_post_125$D,aux_post_125$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_125)
  interim_allocation_125<-rbind(interim_allocation_125,new_r)
  
}
colMeans(df_sample_size)
```

```{r}
#no RAR
interim_ss50<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_50)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_50$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior =as.numeric( df_q_andmu_posteriors_50[i,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.1)
  interim_ss50<-rbind(interim_ss50,interim_aux)
}

colMeans(interim_ss50)

```

```{r}

interim_ss_rar50<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_50)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_50$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_50[i,]),q_prior =as.numeric( df_q_andmu_posteriors_50[i,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.1)
  interim_ss_rar50<-rbind(interim_ss_rar50,interim_aux)
}

colMeans(interim_ss_rar50,na.rm = T)
```

```{r}
#no RAR
interim_ss25<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_25)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_25$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior =as.numeric( df_q_andmu_posteriors_25[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.1)
  interim_ss25<-rbind(interim_ss25,interim_aux)
}

colMeans(interim_ss25)
```

```{r}
interim_ss_rar25<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_25)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_25$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_25[i,]),q_prior =as.numeric( df_q_andmu_posteriors_25[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.1)
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
}

colMeans(interim_ss_rar25,na.rm = T)
```

```{r}
#no RAR
interim_ss125<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_125)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_125$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_125$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior =as.numeric( df_q_andmu_posteriors_125[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.1)
  interim_ss125<-rbind(interim_ss125,interim_aux)
}

colMeans(interim_ss125)
```

```{r}
interim_ss_rar125<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_125)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_125$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_125$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_125[i,]),q_prior =as.numeric( df_q_andmu_posteriors_125[i,grep("q",colnames(df_q_andmu_posteriors_125)),]),
                                       delta_star=0.1)
  interim_ss_rar125<-rbind(interim_ss_rar125,interim_aux)
}

colMeans(interim_ss_rar125,na.rm = T)
```


```{r}
interim_ss_rar25<-tibble()
df_sample_size<-tibble()
interim_ss_rar50<-tibble()
df_q_andmu_posteriors_50<-tibble()
df_alpha_beta_posteriors_50<-tibble()
df_D_posteriors_50<-tibble()
interim_allocation_50<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior=c(1,1,1,1),delta_star=0.1)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment2/4)
  y4_aux=rnorm(round(aux$treatment4/4),mean=0.6, sd=1)
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)
  
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.1)
  if(any(is.na(interim_aux)))next
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
  

  #Scenario 4
  length1<-max(0,round(interim_aux$treatment1/2-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-max(0,round(interim_aux$treatment2/2-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=0, sd=1)
  length3<-max(0,round(interim_aux$treatment3/2-aux$treatment3/4))
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-max(0,round(interim_aux$treatment4/2-aux$treatment4/4))
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),rep(3,length3),rep(4,length4))
  df_50=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_50)
  aux_post_50<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(max(round(aux$treatment1/4),round(interim_aux$treatment1/2)),
                                               max(round(aux$treatment2/4),round(interim_aux$treatment2/2)),
                                               max(round(aux$treatment3/4),round(interim_aux$treatment3/2)),
                                               max(round(aux$treatment4/4),round(interim_aux$treatment4/2))),
                                   y_treatment = df)
  
  df_q_andmu_posteriors_50<-aux_post_50$q_andmu_posteriors
  df_alpha_beta_posteriors_50<-aux_post_50$alpha_beta_params
  df_D_posteriors_50<-aux_post_50$D
  treatment_differences_50<-get_treatment_difference(aux_post_50$q_andmu_posteriors,aux_post_50$D,aux_post_50$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_50)
  interim_allocation_50<-rbind(interim_allocation_50,new_r)
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior,beta_prior = df_alpha_beta_posteriors_50$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_50[,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.1)
    if(any(is.na(interim_aux)))next
   interim_ss_rar50<-rbind(interim_ss_rar50,interim_aux)
  
  
}
colMeans(interim_ss_rar50)
```
```{r}
interim_ss_rar25<-tibble()
df_sample_size<-tibble()
interim_ss_rar75<-tibble()
df_q_andmu_posteriors_75<-tibble()
df_alpha_beta_posteriors_75<-tibble()
df_D_posteriors_75<-tibble()
interim_allocation_75<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior=c(1,1,1,1),delta_star=0.1)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment2/4)
  y4_aux=rnorm(round(aux$treatment4/4),mean=0.6, sd=1)
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)
  
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.1)
  if(any(is.na(interim_aux)))next
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
  

  #Scenario 5
  length1<-max(0,round(interim_aux$treatment1*0.75-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-max(0,round(interim_aux$treatment2*0.75-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-max(0,round(interim_aux$treatment3*0.75-aux$treatment3/4))
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-max(0,round(interim_aux$treatment4*0.75-aux$treatment4/4))
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),rep(3,length3),rep(4,length4))
  df_75=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_75)
  aux_post_75<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(max(round(aux$treatment1/4),round(interim_aux$treatment1*0.75)),
                                               max(round(aux$treatment2/4),round(interim_aux$treatment2*0.75)),
                                               max(round(aux$treatment3/4),round(interim_aux$treatment3*0.75)),
                                               max(round(aux$treatment4/4),round(interim_aux$treatment4*0.75))),
                                   y_treatment = df)
  
  df_q_andmu_posteriors_75<-aux_post_75$q_andmu_posteriors
  df_alpha_beta_posteriors_75<-aux_post_75$alpha_beta_params
  df_D_posteriors_75<-aux_post_75$D
  treatment_differences_75<-get_treatment_difference(aux_post_75$q_andmu_posteriors,aux_post_75$D,aux_post_75$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_75)
  interim_allocation_75<-rbind(interim_allocation_75,new_r)
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_75$alpha_posterior,beta_prior = df_alpha_beta_posteriors_75$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_75[,grep("q",colnames(df_q_andmu_posteriors_75)),]),
                                       delta_star=0.1)
  if(any(is.na(interim_aux)))next
  
   interim_ss_rar75<-rbind(interim_ss_rar75,interim_aux)
  
  
}
colMeans(interim_ss_rar75)
```





## Scenario 6-10

```{r}

beta<-alpha
df_sample_size<-tibble()

df_q_andmu_posteriors_50<-tibble()
df_alpha_beta_posteriors_50<-tibble()
df_D_posteriors_50<-tibble()
interim_allocation_50<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()

df_q_andmu_posteriors_125<-tibble()
df_alpha_beta_posteriors_125<-tibble()
df_D_posteriors_125<-tibble()
interim_allocation_125<-tibble()

for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior=c(1,1,1,1),delta_star=0.2)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 1
  length1<-round(aux$treatment1/2)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/2)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/2)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment4/2)
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_50=tibble(treatment_assignment,y)
  aux_post_50<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_50)
  
  df_q_andmu_posteriors_50<-rbind(df_q_andmu_posteriors_50,aux_post_50$q_andmu_posteriors)
  df_alpha_beta_posteriors_50<-rbind(df_alpha_beta_posteriors_50,aux_post_50$alpha_beta_params)
  df_D_posteriors_50<-rbind(df_D_posteriors_50,aux_post_50$D)
  
  treatment_differences_50<-get_treatment_difference(aux_post_50$q_andmu_posteriors,aux_post_50$D,aux_post_50$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_50)
  interim_allocation_50<-rbind(interim_allocation_50,new_r)

  #Scenario 2
  
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment4/4)
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-rbind(df_q_andmu_posteriors_25,aux_post_25$q_andmu_posteriors)
  df_alpha_beta_posteriors_25<-rbind(df_alpha_beta_posteriors_25,aux_post_25$alpha_beta_params)
  df_D_posteriors_25<-rbind(df_D_posteriors_25,aux_post_25$D)
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)

  
  #Scenario 3
  
  length1<-round(aux$treatment1/8)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/8)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/8)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment4/8)
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_125=tibble(treatment_assignment,y)
  
  aux_post_125<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_125)
  
  df_q_andmu_posteriors_125<-rbind(df_q_andmu_posteriors_125,aux_post_125$q_andmu_posteriors)
  df_alpha_beta_posteriors_125<-rbind(df_alpha_beta_posteriors_125,aux_post_125$alpha_beta_params)
  df_D_posteriors_125<-rbind(df_D_posteriors_125,aux_post_125$D)
  
  treatment_differences_125<-get_treatment_difference(aux_post_125$q_andmu_posteriors,aux_post_125$D,aux_post_125$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_125)
  interim_allocation_125<-rbind(interim_allocation_125,new_r)
  
}
colMeans(df_sample_size)
```

```{r}
#no RAR
interim_ss50<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_50)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_50$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior =as.numeric( df_q_andmu_posteriors_50[i,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.2)
  interim_ss50<-rbind(interim_ss50,interim_aux)
}

colMeans(interim_ss50)

```

```{r}

interim_ss_rar50<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_50)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_50$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_50[i,]),q_prior =as.numeric( df_q_andmu_posteriors_50[i,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.2)
  interim_ss_rar50<-rbind(interim_ss_rar50,interim_aux)
}

colMeans(interim_ss_rar50,na.rm = T)
```

```{r}
#no RAR
interim_ss25<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_25)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_25$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior =as.numeric( df_q_andmu_posteriors_25[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.2)
  interim_ss25<-rbind(interim_ss25,interim_aux)
}

colMeans(interim_ss25)
```

```{r}
interim_ss_rar25<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_25)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_25$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_25[i,]),q_prior =as.numeric( df_q_andmu_posteriors_25[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.2)
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
}

colMeans(interim_ss_rar25,na.rm = T)
```

```{r}
#no RAR
interim_ss125<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_125)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_125$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_125$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior =as.numeric( df_q_andmu_posteriors_125[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.2)
  interim_ss125<-rbind(interim_ss125,interim_aux)
}

colMeans(interim_ss125)
```

```{r}
interim_ss_rar125<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_125)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_125$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_125$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_125[i,]),q_prior =as.numeric( df_q_andmu_posteriors_125[i,grep("q",colnames(df_q_andmu_posteriors_125)),]),
                                       delta_star=0.2)
  interim_ss_rar125<-rbind(interim_ss_rar125,interim_aux)
}

colMeans(interim_ss_rar125,na.rm = T)
```


```{r}
interim_ss_rar25<-tibble()
df_sample_size<-tibble()
interim_ss_rar50<-tibble()
df_q_andmu_posteriors_50<-tibble()
df_alpha_beta_posteriors_50<-tibble()
df_D_posteriors_50<-tibble()
interim_allocation_50<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior=c(1,1,1,1),delta_star=0.2)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment2/4)
  y4_aux=rnorm(round(aux$treatment4/4),mean=0.6, sd=1)
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)
  
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.2)
  if(any(is.na(interim_aux)))next
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
  

  #Scenario 4
  length1<-max(0,round(interim_aux$treatment1/2-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-max(0,round(interim_aux$treatment2/2-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-max(0,round(interim_aux$treatment3/2-aux$treatment3/4))
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-max(0,round(interim_aux$treatment4/2-aux$treatment4/4))
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),rep(3,length3),rep(4,length4))
  df_50=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_50)
  aux_post_50<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(max(round(aux$treatment1/4),round(interim_aux$treatment1/2)),
                                               max(round(aux$treatment2/4),round(interim_aux$treatment2/2)),
                                               max(round(aux$treatment3/4),round(interim_aux$treatment3/2)),
                                               max(round(aux$treatment4/4),round(interim_aux$treatment4/2))),
                                   y_treatment = df)
  
  df_q_andmu_posteriors_50<-aux_post_50$q_andmu_posteriors
  df_alpha_beta_posteriors_50<-aux_post_50$alpha_beta_params
  df_D_posteriors_50<-aux_post_50$D
  treatment_differences_50<-get_treatment_difference(aux_post_50$q_andmu_posteriors,aux_post_50$D,aux_post_50$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_50)
  interim_allocation_50<-rbind(interim_allocation_50,new_r)
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior,beta_prior = df_alpha_beta_posteriors_50$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_50[,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.2)
    if(any(is.na(interim_aux)))next
   interim_ss_rar50<-rbind(interim_ss_rar50,interim_aux)
  
  
}
colMeans(interim_ss_rar50)
```
```{r}
interim_ss_rar25<-tibble()
df_sample_size<-tibble()
interim_ss_rar75<-tibble()
df_q_andmu_posteriors_75<-tibble()
df_alpha_beta_posteriors_75<-tibble()
df_D_posteriors_75<-tibble()
interim_allocation_75<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior=c(1,1,1,1),delta_star=0.2)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment2/4)
  y4_aux=rnorm(round(aux$treatment4/4),mean=0.6, sd=1)
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)
  
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.2)
  if(any(is.na(interim_aux)))next
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
  

  #Scenario 5
  length1<-max(0,round(interim_aux$treatment1*0.75-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-max(0,round(interim_aux$treatment2*0.75-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-max(0,round(interim_aux$treatment3*0.75-aux$treatment3/4))
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-max(0,round(interim_aux$treatment4*0.75-aux$treatment4/4))
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),rep(3,length3),rep(4,length4))
  df_75=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_75)
  aux_post_75<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(max(round(aux$treatment1/4),round(interim_aux$treatment1*0.75)),
                                               max(round(aux$treatment2/4),round(interim_aux$treatment2*0.75)),
                                               max(round(aux$treatment3/4),round(interim_aux$treatment3*0.75)),
                                               max(round(aux$treatment4/4),round(interim_aux$treatment4*0.75))),
                                   y_treatment = df)
  
  df_q_andmu_posteriors_75<-aux_post_75$q_andmu_posteriors
  df_alpha_beta_posteriors_75<-aux_post_75$alpha_beta_params
  df_D_posteriors_75<-aux_post_75$D
  treatment_differences_75<-get_treatment_difference(aux_post_75$q_andmu_posteriors,aux_post_75$D,aux_post_75$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_75)
  interim_allocation_75<-rbind(interim_allocation_75,new_r)
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_75$alpha_posterior,beta_prior = df_alpha_beta_posteriors_75$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_75[,grep("q",colnames(df_q_andmu_posteriors_75)),]),
                                       delta_star=0.2)
  if(any(is.na(interim_aux)))next
  
   interim_ss_rar75<-rbind(interim_ss_rar75,interim_aux)
  
  
}
colMeans(interim_ss_rar75)
```



## Scenario 11-15

```{r}

beta<-alpha
df_sample_size<-tibble()

df_q_andmu_posteriors_50<-tibble()
df_alpha_beta_posteriors_50<-tibble()
df_D_posteriors_50<-tibble()
interim_allocation_50<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()

df_q_andmu_posteriors_125<-tibble()
df_alpha_beta_posteriors_125<-tibble()
df_D_posteriors_125<-tibble()
interim_allocation_125<-tibble()

for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior=c(1,1,1,1),delta_star=0.3)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 1
  length1<-round(aux$treatment1/2)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/2)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/2)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment4/2)
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_50=tibble(treatment_assignment,y)
  aux_post_50<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_50)
  
  df_q_andmu_posteriors_50<-rbind(df_q_andmu_posteriors_50,aux_post_50$q_andmu_posteriors)
  df_alpha_beta_posteriors_50<-rbind(df_alpha_beta_posteriors_50,aux_post_50$alpha_beta_params)
  df_D_posteriors_50<-rbind(df_D_posteriors_50,aux_post_50$D)
  
  treatment_differences_50<-get_treatment_difference(aux_post_50$q_andmu_posteriors,aux_post_50$D,aux_post_50$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_50)
  interim_allocation_50<-rbind(interim_allocation_50,new_r)

  #Scenario 2
  
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment4/4)
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-rbind(df_q_andmu_posteriors_25,aux_post_25$q_andmu_posteriors)
  df_alpha_beta_posteriors_25<-rbind(df_alpha_beta_posteriors_25,aux_post_25$alpha_beta_params)
  df_D_posteriors_25<-rbind(df_D_posteriors_25,aux_post_25$D)
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)

  
  #Scenario 3
  
  length1<-round(aux$treatment1/8)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/8)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/8)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment4/8)
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_125=tibble(treatment_assignment,y)
  
  aux_post_125<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_125)
  
  df_q_andmu_posteriors_125<-rbind(df_q_andmu_posteriors_125,aux_post_125$q_andmu_posteriors)
  df_alpha_beta_posteriors_125<-rbind(df_alpha_beta_posteriors_125,aux_post_125$alpha_beta_params)
  df_D_posteriors_125<-rbind(df_D_posteriors_125,aux_post_125$D)
  
  treatment_differences_125<-get_treatment_difference(aux_post_125$q_andmu_posteriors,aux_post_125$D,aux_post_125$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_125)
  interim_allocation_125<-rbind(interim_allocation_125,new_r)
  
}
colMeans(df_sample_size)
```

```{r}
#no RAR
interim_ss50<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_50)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_50$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior =as.numeric( df_q_andmu_posteriors_50[i,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.3)
  interim_ss50<-rbind(interim_ss50,interim_aux)
}

colMeans(interim_ss50)

```

```{r}

interim_ss_rar50<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_50)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_50$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_50[i,]),q_prior =as.numeric( df_q_andmu_posteriors_50[i,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.3)
  interim_ss_rar50<-rbind(interim_ss_rar50,interim_aux)
}

colMeans(interim_ss_rar50,na.rm = T)
```

```{r}
#no RAR
interim_ss25<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_25)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_25$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior =as.numeric( df_q_andmu_posteriors_25[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.3)
  interim_ss25<-rbind(interim_ss25,interim_aux)
}

colMeans(interim_ss25)
```

```{r}
interim_ss_rar25<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_25)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_25$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_25[i,]),q_prior =as.numeric( df_q_andmu_posteriors_25[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.3)
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
}

colMeans(interim_ss_rar25,na.rm = T)
```

```{r}
#no RAR
interim_ss125<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_125)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_125$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_125$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior =as.numeric( df_q_andmu_posteriors_125[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.3)
  interim_ss125<-rbind(interim_ss125,interim_aux)
}

colMeans(interim_ss125)
```

```{r}
interim_ss_rar125<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_125)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_125$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_125$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_125[i,]),q_prior =as.numeric( df_q_andmu_posteriors_125[i,grep("q",colnames(df_q_andmu_posteriors_125)),]),
                                       delta_star=0.3)
  interim_ss_rar125<-rbind(interim_ss_rar125,interim_aux)
}

colMeans(interim_ss_rar125,na.rm = T)
```


```{r}
interim_ss_rar25<-tibble()
df_sample_size<-tibble()
interim_ss_rar50<-tibble()
df_q_andmu_posteriors_50<-tibble()
df_alpha_beta_posteriors_50<-tibble()
df_D_posteriors_50<-tibble()
interim_allocation_50<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior=c(1,1,1,1),delta_star=0.3)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment2/4)
  y4_aux=rnorm(round(aux$treatment4/4),mean=0.6, sd=1)
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)
  
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.3)
  if(any(is.na(interim_aux)))next
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
  

  #Scenario 4
  length1<-max(0,round(interim_aux$treatment1/2-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-max(0,round(interim_aux$treatment2/2-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-max(0,round(interim_aux$treatment3/2-aux$treatment3/4))
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-max(0,round(interim_aux$treatment4/2-aux$treatment4/4))
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),rep(3,length3),rep(4,length4))
  df_50=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_50)
  aux_post_50<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(max(round(aux$treatment1/4),round(interim_aux$treatment1/2)),
                                               max(round(aux$treatment2/4),round(interim_aux$treatment2/2)),
                                               max(round(aux$treatment3/4),round(interim_aux$treatment3/2)),
                                               max(round(aux$treatment4/4),round(interim_aux$treatment4/2))),
                                   y_treatment = df)
  
  df_q_andmu_posteriors_50<-aux_post_50$q_andmu_posteriors
  df_alpha_beta_posteriors_50<-aux_post_50$alpha_beta_params
  df_D_posteriors_50<-aux_post_50$D
  treatment_differences_50<-get_treatment_difference(aux_post_50$q_andmu_posteriors,aux_post_50$D,aux_post_50$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_50)
  interim_allocation_50<-rbind(interim_allocation_50,new_r)
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior,beta_prior = df_alpha_beta_posteriors_50$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_50[,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.3)
    if(any(is.na(interim_aux)))next
   interim_ss_rar50<-rbind(interim_ss_rar50,interim_aux)
  
  
}
colMeans(interim_ss_rar50)
```
```{r}
interim_ss_rar25<-tibble()
df_sample_size<-tibble()
interim_ss_rar75<-tibble()
df_q_andmu_posteriors_75<-tibble()
df_alpha_beta_posteriors_75<-tibble()
df_D_posteriors_75<-tibble()
interim_allocation_75<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior=c(1,1,1,1),delta_star=0.3)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-round(aux$treatment2/4)
  y4_aux=rnorm(round(aux$treatment4/4),mean=0.6, sd=1)
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)
  
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.3)
  if(any(is.na(interim_aux)))next
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
  

  #Scenario 5
  length1<-max(0,round(interim_aux$treatment1*0.75-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=0, sd=1)
  length2<-max(0,round(interim_aux$treatment2*0.75-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=0.1, sd=1)
  length3<-max(0,round(interim_aux$treatment3*0.75-aux$treatment3/4))
  y3_aux=rnorm(length3,mean=0.2, sd=1)
  length4<-max(0,round(interim_aux$treatment4*0.75-aux$treatment4/4))
  y4_aux=rnorm(length4,mean=0.6, sd=1)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),rep(3,length3),rep(4,length4))
  df_75=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_75)
  aux_post_75<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(max(round(aux$treatment1/4),round(interim_aux$treatment1*0.75)),
                                               max(round(aux$treatment2/4),round(interim_aux$treatment2*0.75)),
                                               max(round(aux$treatment3/4),round(interim_aux$treatment3*0.75)),
                                               max(round(aux$treatment4/4),round(interim_aux$treatment4*0.75))),
                                   y_treatment = df)
  
  df_q_andmu_posteriors_75<-aux_post_75$q_andmu_posteriors
  df_alpha_beta_posteriors_75<-aux_post_75$alpha_beta_params
  df_D_posteriors_75<-aux_post_75$D
  treatment_differences_75<-get_treatment_difference(aux_post_75$q_andmu_posteriors,aux_post_75$D,aux_post_75$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_75)
  interim_allocation_75<-rbind(interim_allocation_75,new_r)
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_75$alpha_posterior,beta_prior = df_alpha_beta_posteriors_75$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_75[,grep("q",colnames(df_q_andmu_posteriors_75)),]),
                                       delta_star=0.3)
  if(any(is.na(interim_aux)))next
  
   interim_ss_rar75<-rbind(interim_ss_rar75,interim_aux)
  
  
}
colMeans(interim_ss_rar75)
```

#Scenario 16-20
# Lecanemab

From study protocol:

"The sample size for this study is estimated based on comparison of BAN2401 versus placebo with respect to the primary efficacy endpoint, the change from baseline in CDR-SB at 18 months. Based on data from BAN2401 Phase 2 study BAN2401-G000-201, an estimated standard deviation of the change from baseline CDR-SB at 18 months in placebo is 2.031 and an estimated treatment difference is 0.373 in all subjects. Therefore, assuming an estimated 20% dropout rate at 18 months in this study, a total sample size of 1566 subjects, including 783 subjects in placebo and 783 subjects in BAN2401, will have 90% power to detect the treatment difference between BAN2401 and placebo in all subjects using a 2-sample t-test at a significance level of 2-sided alpha = 0.05."

From sample size rationale: sd=2.031 variance is 4.124961, so nu_prior is 0.2424265 , so alpha/beta is 0.2424265

From collected data: SE=0.1122449 N=1795 , so SD=4.755529 (SE\*sqrt(N)), Mean Change=0.45, so treatment effect size is 0.0946267
```{r}
beta<-alpha/0.2424265
df_sample_size<-tibble()

df_q_andmu_posteriors_50<-tibble()
df_alpha_beta_posteriors_50<-tibble()
df_D_posteriors_50<-tibble()
interim_allocation_50<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()

df_q_andmu_posteriors_125<-tibble()
df_alpha_beta_posteriors_125<-tibble()
df_D_posteriors_125<-tibble()
interim_allocation_125<-tibble()

for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(0.5, 0.5),q_prior=c(1,1),delta_star=0.373)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 1
  length1<-round(aux$treatment1/2)
  y1_aux=rnorm(length1,mean=0.45, sd=4.755529)
  length2<-round(aux$treatment2/2)
  y2_aux=rnorm(length2,mean=0, sd=4.755529)
 
  
  y=c(y1_aux,y2_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2))
  df_50=tibble(treatment_assignment,y)
  aux_post_50<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1),mu_prior=c(0,0),
                                   N_treat = c(length1,length2),
                                   y_treatment = df_50)
  
  df_q_andmu_posteriors_50<-rbind(df_q_andmu_posteriors_50,aux_post_50$q_andmu_posteriors)
  df_alpha_beta_posteriors_50<-rbind(df_alpha_beta_posteriors_50,aux_post_50$alpha_beta_params)
  df_D_posteriors_50<-rbind(df_D_posteriors_50,aux_post_50$D)
  
  treatment_differences_50<-get_treatment_difference(aux_post_50$q_andmu_posteriors,aux_post_50$D,aux_post_50$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_50)
  interim_allocation_50<-rbind(interim_allocation_50,new_r)

  #Scenario 2
  
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=0.45, sd=4.755529)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0, sd=4.755529)
 
  
  y=c(y1_aux,y2_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2))
  
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1),mu_prior=c(0,0),
                                   N_treat = c(length1,length2),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-rbind(df_q_andmu_posteriors_25,aux_post_25$q_andmu_posteriors)
  df_alpha_beta_posteriors_25<-rbind(df_alpha_beta_posteriors_25,aux_post_25$alpha_beta_params)
  df_D_posteriors_25<-rbind(df_D_posteriors_25,aux_post_25$D)
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)

  
  #Scenario 3
  
 length1<-round(aux$treatment1/8)
  y1_aux=rnorm(length1,mean=0.45, sd=4.755529)
  length2<-round(aux$treatment2/8)
  y2_aux=rnorm(length2,mean=0, sd=4.755529)
 
  
  y=c(y1_aux,y2_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2))

  df_125=tibble(treatment_assignment,y)
  
  aux_post_125<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1),mu_prior=c(0,0),
                                   N_treat = c(length1,length2),
                                   y_treatment = df_125)
  
  df_q_andmu_posteriors_125<-rbind(df_q_andmu_posteriors_125,aux_post_125$q_andmu_posteriors)
  df_alpha_beta_posteriors_125<-rbind(df_alpha_beta_posteriors_125,aux_post_125$alpha_beta_params)
  df_D_posteriors_125<-rbind(df_D_posteriors_125,aux_post_125$D)
  
  treatment_differences_125<-get_treatment_difference(aux_post_125$q_andmu_posteriors,aux_post_125$D,aux_post_125$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_125)
  interim_allocation_125<-rbind(interim_allocation_125,new_r)
  
}
colMeans(df_sample_size)
```

```{r}
#no RAR
interim_ss50<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_50)){
  interim_aux<-sample_size_calculation(alpha_prior=df_alpha_beta_posteriors_50$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_50$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/2,1/2),q_prior =as.numeric( df_q_andmu_posteriors_50[i,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.373)
  interim_ss50<-rbind(interim_ss50,interim_aux)
}

colMeans(interim_ss50)

```

```{r}

interim_ss_rar50<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_50)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_50$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_50[i,]),q_prior =as.numeric( df_q_andmu_posteriors_50[i,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.373)
  interim_ss_rar50<-rbind(interim_ss_rar50,interim_aux)
}

colMeans(interim_ss_rar50,na.rm = T)
```

```{r}
#no RAR
interim_ss25<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_25)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_25$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/2,1/2),q_prior =as.numeric( df_q_andmu_posteriors_25[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.373)
  interim_ss25<-rbind(interim_ss25,interim_aux)
}

colMeans(interim_ss25)
```

```{r}
interim_ss_rar25<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_25)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_25$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_25[i,]),q_prior =as.numeric( df_q_andmu_posteriors_25[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.373)
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
}

colMeans(interim_ss_rar25,na.rm = T)
```

```{r}
#no RAR
interim_ss125<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_125)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_125$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_125$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/2,1/2),q_prior =as.numeric( df_q_andmu_posteriors_125[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.373)
  interim_ss125<-rbind(interim_ss125,interim_aux)
}

colMeans(interim_ss125)
```

```{r}
interim_ss_rar125<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_125)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_125$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_125$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_125[i,]),q_prior =as.numeric( df_q_andmu_posteriors_125[i,grep("q",colnames(df_q_andmu_posteriors_125)),]),
                                       delta_star=0.373)
  interim_ss_rar125<-rbind(interim_ss_rar125,interim_aux)
}

colMeans(interim_ss_rar125,na.rm = T)
```


```{r}
interim_ss_rar25<-tibble()
df_sample_size<-tibble()
interim_ss_rar50<-tibble()
df_q_andmu_posteriors_50<-tibble()
df_alpha_beta_posteriors_50<-tibble()
df_D_posteriors_50<-tibble()
interim_allocation_50<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/2,1/2),q_prior=c(1,1),delta_star=0.373)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=0, sd=4.755529)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.45, sd=4.755529)
 
  y=c(y1_aux,y2_aux)
  
  treatment_assignment<-c(rep(1,length1),rep(2,length2))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1),mu_prior=c(0,0),
                                   N_treat = c(length1,length2),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)
  
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.373)
  if(any(is.na(interim_aux)))next
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
  

  #Scenario 4
  length1<-max(0,round(interim_aux$treatment1/2-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=0, sd=4.755529)
  length2<-max(0,round(interim_aux$treatment2/2-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=0.45, sd=4.755529)
  
  
  y=c(y1_aux,y2_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2))
  df_50=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_50)
  aux_post_50<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1),mu_prior=c(0,0),
                                   N_treat = c(max(round(aux$treatment1/4),round(interim_aux$treatment1/2)),
                                               max(round(aux$treatment2/4),round(interim_aux$treatment2/2))),
                                   y_treatment = df)
  
  df_q_andmu_posteriors_50<-aux_post_50$q_andmu_posteriors
  df_alpha_beta_posteriors_50<-aux_post_50$alpha_beta_params
  df_D_posteriors_50<-aux_post_50$D
  treatment_differences_50<-get_treatment_difference(aux_post_50$q_andmu_posteriors,aux_post_50$D,aux_post_50$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_50)
  interim_allocation_50<-rbind(interim_allocation_50,new_r)
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior,beta_prior = df_alpha_beta_posteriors_50$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_50[,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.373)
    if(any(is.na(interim_aux)))next
   interim_ss_rar50<-rbind(interim_ss_rar50,interim_aux)
  
  
}
colMeans(interim_ss_rar50)
```

```{r}
interim_ss_rar25<-tibble()
df_sample_size<-tibble()
interim_ss_rar75<-tibble()
df_q_andmu_posteriors_75<-tibble()
df_alpha_beta_posteriors_75<-tibble()
df_D_posteriors_75<-tibble()
interim_allocation_75<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/2,1/2),q_prior=c(1,1),delta_star=0.373)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=0, sd=4.755529)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.45, sd=4.755529)
  y=c(y1_aux,y2_aux)
  
  treatment_assignment<-c(rep(1,length1),rep(2,length2))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1),mu_prior=c(0,0),
                                   N_treat = c(length1,length2),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)
  
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.373)
  if(any(is.na(interim_aux)))next
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
  

  #Scenario 5
  length1<-max(0,round(interim_aux$treatment1*0.75-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=0, sd=4.755529)
  length2<-max(0,round(interim_aux$treatment2*0.75-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=0.45, sd=4.755529)
  
  y=c(y1_aux,y2_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2))
  df_75=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_75)
  aux_post_75<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1),mu_prior=c(0,0),
                                   N_treat = c(max(round(aux$treatment1/4),round(interim_aux$treatment1*0.75)),
                                               max(round(aux$treatment2/4),round(interim_aux$treatment2*0.75)),
                                               max(round(aux$treatment3/4),round(interim_aux$treatment3*0.75)),
                                               max(round(aux$treatment4/4),round(interim_aux$treatment4*0.75))),
                                   y_treatment = df)
  
  df_q_andmu_posteriors_75<-aux_post_75$q_andmu_posteriors
  df_alpha_beta_posteriors_75<-aux_post_75$alpha_beta_params
  df_D_posteriors_75<-aux_post_75$D
  treatment_differences_75<-get_treatment_difference(aux_post_75$q_andmu_posteriors,aux_post_75$D,aux_post_75$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_75)
  interim_allocation_75<-rbind(interim_allocation_75,new_r)
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_75$alpha_posterior,beta_prior = df_alpha_beta_posteriors_75$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_75[,grep("q",colnames(df_q_andmu_posteriors_75)),]),
                                       delta_star=0.373)
  if(any(is.na(interim_aux)))next
  
   interim_ss_rar75<-rbind(interim_ss_rar75,interim_aux)
  
  
}
colMeans(interim_ss_rar75)
```


#Tideglusib

"A previous pilot study had shown a clinically relevant difference between active and placebo arms [25]
of 4.7 point (SD 7.3) in ADAS-cog15, equivalent to the expected natural decline for 6 months [30]. Power
calculations showed that a sample of 280 patients (40 patients in the 500 mgQDarm and 80 in the other treatment
arms), assuming a 30% drop-out rate, provided 90% statistical power to detect a 4.5 point difference
in the ADAS-cog15 between each treatment and placebo group according to standard formulae based on Students t-test."

From the paper, SD=7.3 =>variance=53.29 so precision is 0.01876525 so alpha/beta is 0.01876525. Clinically meaningful difference is 4.5/7.3=0.6164384
From table 2, placebo has parameters 1.7, 6.9 sd; trt 1 0.2, 6.7; trt2 1.4, 6.6; trt3 2.6 and 7.4.

```{r}

beta<-alpha/0.01876525
df_sample_size<-tibble()

df_q_andmu_posteriors_50<-tibble()
df_alpha_beta_posteriors_50<-tibble()
df_D_posteriors_50<-tibble()
interim_allocation_50<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()

df_q_andmu_posteriors_125<-tibble()
df_alpha_beta_posteriors_125<-tibble()
df_D_posteriors_125<-tibble()
interim_allocation_125<-tibble()

for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior=c(1,1,1,1),delta_star=0.6164384)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 1
  length1<-round(aux$treatment1/2)
  y1_aux=rnorm(length1,mean=1.7, sd=6.9)
  length2<-round(aux$treatment2/2)
  y2_aux=rnorm(length2,mean=0.2, sd=6.7)
  length3<-round(aux$treatment3/2)
  y3_aux=rnorm(length3,mean=1.4, sd=6.6)
  length4<-round(aux$treatment4/2)
  y4_aux=rnorm(length4,mean=2.6, sd=7.4)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_50=tibble(treatment_assignment,y)
  aux_post_50<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_50)
  
  df_q_andmu_posteriors_50<-rbind(df_q_andmu_posteriors_50,aux_post_50$q_andmu_posteriors)
  df_alpha_beta_posteriors_50<-rbind(df_alpha_beta_posteriors_50,aux_post_50$alpha_beta_params)
  df_D_posteriors_50<-rbind(df_D_posteriors_50,aux_post_50$D)
  
  treatment_differences_50<-get_treatment_difference(aux_post_50$q_andmu_posteriors,aux_post_50$D,aux_post_50$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_50)
  interim_allocation_50<-rbind(interim_allocation_50,new_r)

  #Scenario 2
  
 length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=1.7, sd=6.9)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.2, sd=6.7)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=1.4, sd=6.6)
  length4<-round(aux$treatment4/4)
  y4_aux=rnorm(length4,mean=2.6, sd=7.4)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-rbind(df_q_andmu_posteriors_25,aux_post_25$q_andmu_posteriors)
  df_alpha_beta_posteriors_25<-rbind(df_alpha_beta_posteriors_25,aux_post_25$alpha_beta_params)
  df_D_posteriors_25<-rbind(df_D_posteriors_25,aux_post_25$D)
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)

  
  #Scenario 3
  
 length1<-round(aux$treatment1/8)
  y1_aux=rnorm(length1,mean=1.7, sd=6.9)
  length2<-round(aux$treatment2/8)
  y2_aux=rnorm(length2,mean=0.2, sd=6.7)
  length3<-round(aux$treatment3/8)
  y3_aux=rnorm(length3,mean=1.4, sd=6.6)
  length4<-round(aux$treatment4/8)
  y4_aux=rnorm(length4,mean=2.6, sd=7.4)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_125=tibble(treatment_assignment,y)
  
  aux_post_125<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_125)
  
  df_q_andmu_posteriors_125<-rbind(df_q_andmu_posteriors_125,aux_post_125$q_andmu_posteriors)
  df_alpha_beta_posteriors_125<-rbind(df_alpha_beta_posteriors_125,aux_post_125$alpha_beta_params)
  df_D_posteriors_125<-rbind(df_D_posteriors_125,aux_post_125$D)
  
  treatment_differences_125<-get_treatment_difference(aux_post_125$q_andmu_posteriors,aux_post_125$D,aux_post_125$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_125)
  interim_allocation_125<-rbind(interim_allocation_125,new_r)
  
}
colMeans(df_sample_size)
```

```{r}
#no RAR
interim_ss50<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_50)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_50$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior =as.numeric( df_q_andmu_posteriors_50[i,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.6164384)
  interim_ss50<-rbind(interim_ss50,interim_aux)
}

colMeans(interim_ss50)

```

```{r}

interim_ss_rar50<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_50)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_50$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_50[i,]),q_prior =as.numeric( df_q_andmu_posteriors_50[i,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.6164384)
  interim_ss_rar50<-rbind(interim_ss_rar50,interim_aux)
}

colMeans(interim_ss_rar50,na.rm = T)
```

```{r}
#no RAR
interim_ss25<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_25)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_25$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior =as.numeric( df_q_andmu_posteriors_25[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.6164384)
  interim_ss25<-rbind(interim_ss25,interim_aux)
}

colMeans(interim_ss25)
```

```{r}
interim_ss_rar25<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_25)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_25$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_25[i,]),q_prior =as.numeric( df_q_andmu_posteriors_25[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.6164384)
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
}

colMeans(interim_ss_rar25,na.rm = T)
```

```{r}
#no RAR
interim_ss125<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_125)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_125$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_125$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior =as.numeric( df_q_andmu_posteriors_125[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.6164384)
  interim_ss125<-rbind(interim_ss125,interim_aux)
}

colMeans(interim_ss125)
```

```{r}
interim_ss_rar125<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_125)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_125$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_125$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_125[i,]),q_prior =as.numeric( df_q_andmu_posteriors_125[i,grep("q",colnames(df_q_andmu_posteriors_125)),]),
                                       delta_star=0.6164384)
  interim_ss_rar125<-rbind(interim_ss_rar125,interim_aux)
}

colMeans(interim_ss_rar125,na.rm = T)
```


```{r}
interim_ss_rar25<-tibble()
df_sample_size<-tibble()
interim_ss_rar50<-tibble()
df_q_andmu_posteriors_50<-tibble()
df_alpha_beta_posteriors_50<-tibble()
df_D_posteriors_50<-tibble()
interim_allocation_50<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior=c(1,1,1,1),delta_star=0.6164384)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=1.7, sd=6.9)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.2, sd=6.7)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=1.4, sd=6.6)
  length4<-round(aux$treatment4/4)
  y4_aux=rnorm(length4,mean=2.6, sd=7.4)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)
  
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.6164384)
  if(any(is.na(interim_aux)))next
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
  

  #Scenario 4
  length1<-max(0,round(interim_aux$treatment1/2-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=1.7, sd=6.9)
  length2<-max(0,round(interim_aux$treatment2/2-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=0.2, sd=6.7)
  length3<-max(0,round(interim_aux$treatment3/2-aux$treatment3/4))
  y3_aux=rnorm(length3,mean=1.4, sd=6.6)
  length4<-max(0,round(interim_aux$treatment4/2-aux$treatment4/4))
  y4_aux=rnorm(length4,mean=2.6, sd=7.4)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),rep(3,length3),rep(4,length4))
  df_50=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_50)
  aux_post_50<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(max(round(aux$treatment1/4),round(interim_aux$treatment1/2)),
                                               max(round(aux$treatment2/4),round(interim_aux$treatment2/2)),
                                               max(round(aux$treatment3/4),round(interim_aux$treatment3/2)),
                                               max(round(aux$treatment4/4),round(interim_aux$treatment4/2))),
                                   y_treatment = df)
  
  df_q_andmu_posteriors_50<-aux_post_50$q_andmu_posteriors
  df_alpha_beta_posteriors_50<-aux_post_50$alpha_beta_params
  df_D_posteriors_50<-aux_post_50$D
  treatment_differences_50<-get_treatment_difference(aux_post_50$q_andmu_posteriors,aux_post_50$D,aux_post_50$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_50)
  interim_allocation_50<-rbind(interim_allocation_50,new_r)
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior,beta_prior = df_alpha_beta_posteriors_50$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_50[,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=0.6164384)
    if(any(is.na(interim_aux)))next
   interim_ss_rar50<-rbind(interim_ss_rar50,interim_aux)
  
  
}
colMeans(interim_ss_rar50)
```
```{r}
interim_ss_rar25<-tibble()
df_sample_size<-tibble()
interim_ss_rar75<-tibble()
df_q_andmu_posteriors_75<-tibble()
df_alpha_beta_posteriors_75<-tibble()
df_D_posteriors_75<-tibble()
interim_allocation_75<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(1/4,1/4,1/4,1/4),q_prior=c(1,1,1,1),delta_star=0.6164384)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=1.7, sd=6.9)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=0.2, sd=6.7)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=1.4, sd=6.6)
  length4<-round(aux$treatment2/4)
  y4_aux=rnorm(round(aux$treatment4/4),mean=2.6, sd=7.4)
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)
  
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=0.6164384)
  if(any(is.na(interim_aux)))next
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
  

  #Scenario 5
  length1<-max(0,round(interim_aux$treatment1*0.75-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=1.7, sd=6.9)
  length2<-max(0,round(interim_aux$treatment2*0.75-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=0.2, sd=6.7)
  length3<-max(0,round(interim_aux$treatment3*0.75-aux$treatment3/4))
  y3_aux=rnorm(length3,mean=1.4, sd=6.6)
  length4<-max(0,round(interim_aux$treatment4*0.75-aux$treatment4/4))
  y4_aux=rnorm(length4,mean=2.6, sd=7.4)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),rep(3,length3),rep(4,length4))
  df_75=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_75)
  aux_post_75<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(max(round(aux$treatment1/4),round(interim_aux$treatment1*0.75)),
                                               max(round(aux$treatment2/4),round(interim_aux$treatment2*0.75)),
                                               max(round(aux$treatment3/4),round(interim_aux$treatment3*0.75)),
                                               max(round(aux$treatment4/4),round(interim_aux$treatment4*0.75))),
                                   y_treatment = df)
  
  df_q_andmu_posteriors_75<-aux_post_75$q_andmu_posteriors
  df_alpha_beta_posteriors_75<-aux_post_75$alpha_beta_params
  df_D_posteriors_75<-aux_post_75$D
  treatment_differences_75<-get_treatment_difference(aux_post_75$q_andmu_posteriors,aux_post_75$D,aux_post_75$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_75)
  interim_allocation_75<-rbind(interim_allocation_75,new_r)
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_75$alpha_posterior,beta_prior = df_alpha_beta_posteriors_75$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_75[,grep("q",colnames(df_q_andmu_posteriors_75)),]),
                                       delta_star=0.6164384)
  if(any(is.na(interim_aux)))next
  
   interim_ss_rar75<-rbind(interim_ss_rar75,interim_aux)
  
  
}
colMeans(interim_ss_rar75)
```

