---
title: "Tideglusib"
author: "Vahan Aslanyan"
format: pdf
editor: visual
---

```{r}
set.seed(219)
source("bayesian_ssr.R")
```

# Tideglusib

"A previous pilot study had shown a clinically relevant difference between active and placebo arms \[25\] of 4.7 point (SD 7.3) in ADAS-cog15, equivalent to the expected natural decline for 6 months \[30\]. Power calculations showed that a sample of 280 patients (40 patients in the 500 mgQDarm and 80 in the other treatment arms), assuming a 30% drop-out rate, provided 90% statistical power to detect a 4.5 point difference in the ADAS-cog15 between each treatment and placebo group according to standard formulae based on Student's t-test."

From the paper, SD=7.3 =\>variance=53.29 so precision is 0.01876525 so alpha/beta is 0.01876525. Clinically meaningful difference is 4.5/7.3=0.6164384. From table 2, placebo has parameters 1.7, 6.9 sd; trt 1 0.2, 6.7; trt2 1.4, 6.6; trt3 2.6 and 7.4.

### Scenario 21-25

```{r}
alpha<-runif(5000,0,20)
beta<-alpha/0.01876525
df_sample_size<-tibble()

df_q_andmu_posteriors_50<-tibble()
df_alpha_beta_posteriors_50<-tibble()
df_D_posteriors_50<-tibble()
interim_allocation_50<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()

df_q_andmu_posteriors_125<-tibble()
df_alpha_beta_posteriors_125<-tibble()
df_D_posteriors_125<-tibble()
interim_allocation_125<-tibble()

for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(2/7,1/7,2/7,2/7),q_prior=c(1,1,1,1),delta_star=4.5)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 1
  length1<-round(aux$treatment1/2)
  y1_aux=rnorm(length1,mean=-1.7, sd=6.9)
  length2<-round(aux$treatment2/2)
  y2_aux=rnorm(length2,mean=-0.2, sd=6.7)
  length3<-round(aux$treatment3/2)
  y3_aux=rnorm(length3,mean=-1.4, sd=6.6)
  length4<-round(aux$treatment4/2)
  y4_aux=rnorm(length4,mean=-2.6, sd=7.4)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_50=tibble(treatment_assignment,y)
  aux_post_50<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_50)
  
  df_q_andmu_posteriors_50<-rbind(df_q_andmu_posteriors_50,aux_post_50$q_andmu_posteriors)
  df_alpha_beta_posteriors_50<-rbind(df_alpha_beta_posteriors_50,aux_post_50$alpha_beta_params)
  df_D_posteriors_50<-rbind(df_D_posteriors_50,aux_post_50$D)
  
  treatment_differences_50<-get_treatment_difference(aux_post_50$q_andmu_posteriors,aux_post_50$D,aux_post_50$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_50)
  interim_allocation_50<-rbind(interim_allocation_50,new_r)

  #Scenario 2
  
 length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=-1.7, sd=6.9)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=-0.2, sd=6.7)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=-1.4, sd=6.6)
  length4<-round(aux$treatment4/4)
  y4_aux=rnorm(length4,mean=-2.6, sd=7.4)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-rbind(df_q_andmu_posteriors_25,aux_post_25$q_andmu_posteriors)
  df_alpha_beta_posteriors_25<-rbind(df_alpha_beta_posteriors_25,aux_post_25$alpha_beta_params)
  df_D_posteriors_25<-rbind(df_D_posteriors_25,aux_post_25$D)
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)

  
  #Scenario 3
  
 length1<-round(aux$treatment1/8)
  y1_aux=rnorm(length1,mean=-1.7, sd=6.9)
  length2<-round(aux$treatment2/8)
  y2_aux=rnorm(length2,mean=-0.2, sd=6.7)
  length3<-round(aux$treatment3/8)
  y3_aux=rnorm(length3,mean=-1.4, sd=6.6)
  length4<-round(aux$treatment4/8)
  y4_aux=rnorm(length4,mean=-2.6, sd=7.4)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_125=tibble(treatment_assignment,y)
  
  aux_post_125<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_125)
  
  df_q_andmu_posteriors_125<-rbind(df_q_andmu_posteriors_125,aux_post_125$q_andmu_posteriors)
  df_alpha_beta_posteriors_125<-rbind(df_alpha_beta_posteriors_125,aux_post_125$alpha_beta_params)
  df_D_posteriors_125<-rbind(df_D_posteriors_125,aux_post_125$D)
  
  treatment_differences_125<-get_treatment_difference(aux_post_125$q_andmu_posteriors,aux_post_125$D,aux_post_125$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_125)
  interim_allocation_125<-rbind(interim_allocation_125,new_r)
  
}
colMeans(df_sample_size)
```

### Scenario 21 no RAR

```{r}
#no RAR
interim_ss50<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_50)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_50$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(2/7,1/7,2/7,2/7),q_prior =as.numeric( df_q_andmu_posteriors_50[i,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=4.5)
  interim_ss50<-rbind(interim_ss50,interim_aux)
}

colMeans(interim_ss50)+colMeans(df_sample_size)/2
```

### Scenario 21 RAR

```{r}

interim_ss_rar50<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_50)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_50$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_50[i,]),q_prior =as.numeric( df_q_andmu_posteriors_50[i,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=4.5)
  interim_ss_rar50<-rbind(interim_ss_rar50,interim_aux)
}

colMeans(interim_ss_rar50,na.rm = T)+colMeans(df_sample_size)/2
```

### Scenario 22 no RAR

```{r}
#no RAR
interim_ss25<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_25)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_25$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(2/7,1/7,2/7,2/7),q_prior =as.numeric( df_q_andmu_posteriors_25[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=4.5)
  interim_ss25<-rbind(interim_ss25,interim_aux)
}

colMeans(interim_ss25)+colMeans(df_sample_size)/2
```

### Scenario 22 RAR

```{r}
interim_ss_rar25<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_25)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_25$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_25[i,]),q_prior =as.numeric( df_q_andmu_posteriors_25[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=4.5)
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
}

colMeans(interim_ss_rar25,na.rm = T)+colMeans(df_sample_size)/2
```

### Scenario 23 no RAR

```{r}
#no RAR
interim_ss125<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_125)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_125$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_125$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(2/7,1/7,2/7,2/7),q_prior =as.numeric( df_q_andmu_posteriors_125[i,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=4.5)
  interim_ss125<-rbind(interim_ss125,interim_aux)
}

colMeans(interim_ss125)+colMeans(df_sample_size)/2
```

### Scenario 23 RAR

```{r}
interim_ss_rar125<-tibble()
for(i in 1:nrow(df_alpha_beta_posteriors_125)){
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_125$alpha_posterior[i],beta_prior = df_alpha_beta_posteriors_125$beta_posterior[i], eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(interim_allocation_125[i,]),q_prior =as.numeric( df_q_andmu_posteriors_125[i,grep("q",colnames(df_q_andmu_posteriors_125)),]),
                                       delta_star=4.5)
  interim_ss_rar125<-rbind(interim_ss_rar125,interim_aux)
}

colMeans(interim_ss_rar125,na.rm = T)+colMeans(df_sample_size)/2
```

### Scenario 24 RAR

```{r}
interim_ss_rar25<-tibble()
df_sample_size<-tibble()
interim_ss_rar50<-tibble()
df_q_andmu_posteriors_50<-tibble()
df_alpha_beta_posteriors_50<-tibble()
df_D_posteriors_50<-tibble()
interim_allocation_50<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(2/7,1/7,2/7,2/7),q_prior=c(1,1,1,1),delta_star=4.5)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=-1.7, sd=6.9)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=-0.2, sd=6.7)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=-1.4, sd=6.6)
  length4<-round(aux$treatment4/4)
  y4_aux=rnorm(length4,mean=-2.6, sd=7.4)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  df_25=tibble(treatment_assignment,y)
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=4.5)
  if(any(is.na(interim_aux)))next

  recruited_so_far<-aux/4
  interim_aux<-interim_aux+recruited_so_far
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
  

  #Scenario 4
  length1<-max(0,round((interim_aux$treatment1)/2-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=-1.7, sd=6.9)
  length2<-max(0,round((interim_aux$treatment2)/2-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=-0.2, sd=6.7)
  length3<-max(0,round((interim_aux$treatment3)/2-aux$treatment3/4))
  y3_aux=rnorm(length3,mean=-1.4, sd=6.6)
  length4<-max(0,round((interim_aux$treatment4)/2-aux$treatment4/4))
  y4_aux=rnorm(length4,mean=-2.6, sd=7.4)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),rep(3,length3),rep(4,length4))
  df_50=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_50)
  recruited_so_far<-recruited_so_far+c(length1,length2,length3,length4)
  aux_post_50<-posterior_calculations(alpha_prior=df_alpha_beta_posteriors_25$alpha_posterior,
                                      beta_prior=df_alpha_beta_posteriors_25$beta_posterior,
                                      q_prior=as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                      mu_prior=as.numeric( df_q_andmu_posteriors_25[,grep("mu",colnames(df_q_andmu_posteriors_25)),]),
                                   N_treat = c(round(aux$treatment1/4+length1),
                                              round(aux$treatment2/4+length2),
                                              round(aux$treatment3/4+length3),
                                              round(aux$treatment1/4+length4)),
                                   y_treatment = df)
  df_q_andmu_posteriors_50<-aux_post_50$q_andmu_posteriors
  df_alpha_beta_posteriors_50<-aux_post_50$alpha_beta_params
  df_D_posteriors_50<-aux_post_50$D
  treatment_differences_50<-get_treatment_difference(aux_post_50$q_andmu_posteriors,aux_post_50$D,aux_post_50$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_50)
  interim_allocation_50<-rbind(interim_allocation_50,new_r)
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior,beta_prior = df_alpha_beta_posteriors_50$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_50[,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=4.5)
    if(any(is.na(interim_aux)))next
    interim_aux<-interim_aux+recruited_so_far
    interim_ss_rar50<-rbind(interim_ss_rar50,interim_aux)
  
}
colMeans(interim_ss_rar50)
```

### Scenario 25 RAR

```{r}
interim_ss_rar25<-tibble()
df_sample_size<-tibble()
interim_ss_rar75<-tibble()
df_q_andmu_posteriors_75<-tibble()
df_alpha_beta_posteriors_75<-tibble()
df_D_posteriors_75<-tibble()
interim_allocation_75<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(2/7,1/7,2/7,2/7),q_prior=c(1,1,1,1),delta_star=4.5)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=-1.7, sd=6.9)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=-0.2, sd=6.7)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=-1.4, sd=6.6)
  length4<-round(aux$treatment4/4)
  y4_aux=rnorm(length4,mean=-2.6, sd=7.4)
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D
  
  treatment_differences_25<-get_treatment_difference(aux_post_25$q_andmu_posteriors,aux_post_25$D,aux_post_25$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_25)
  interim_allocation_25<-rbind(interim_allocation_25,new_r)
  
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=4.5)
  if(any(is.na(interim_aux)))next
  interim_aux<-interim_aux+aux/4
  interim_ss_rar25<-rbind(interim_ss_rar25,interim_aux)
  

  #Scenario 5
  length1<-max(0,round((interim_aux$treatment1)*0.75-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=-1.7, sd=6.9)
  length2<-max(0,round((interim_aux$treatment2)*0.75-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=-0.2, sd=6.7)
  length3<-max(0,round((interim_aux$treatment3)*0.75-aux$treatment3/4))
  y3_aux=rnorm(length3,mean=-1.4, sd=6.6)
  length4<-max(0,round((interim_aux$treatment4)*0.75-aux$treatment4/4))
  y4_aux=rnorm(length4,mean=-2.6, sd=7.4)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),rep(3,length3),rep(4,length4))
  df_75=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_75)
  aux_post_75<-posterior_calculations(alpha_prior=df_alpha_beta_posteriors_25$alpha_posterior,
                                      beta_prior=df_alpha_beta_posteriors_25$beta_posterior,
                                      q_prior=as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                      mu_prior=as.numeric( df_q_andmu_posteriors_25[,grep("mu",colnames(df_q_andmu_posteriors_25)),]),
                                  N_treat = c(round(interim_aux$treatment1*0.75),
                                              round(interim_aux$treatment2*0.75),
                                              round(interim_aux$treatment3*0.75),
                                              round(interim_aux$treatment4*0.75)),
                                   y_treatment = df)
   sample_sizes_before75<-interim_aux*0.75
  df_q_andmu_posteriors_75<-aux_post_75$q_andmu_posteriors
  df_alpha_beta_posteriors_75<-aux_post_75$alpha_beta_params
  df_D_posteriors_75<-aux_post_75$D
  treatment_differences_75<-get_treatment_difference(aux_post_75$q_andmu_posteriors,aux_post_75$D,aux_post_75$alpha_beta_params)
  new_r<-allocation_calculation(treatment_differences_75)
  interim_allocation_75<-rbind(interim_allocation_75,new_r)
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_75$alpha_posterior,beta_prior = df_alpha_beta_posteriors_75$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=as.numeric(new_r),q_prior =as.numeric( df_q_andmu_posteriors_75[,grep("q",colnames(df_q_andmu_posteriors_75)),]),
                                       delta_star=4.5)
  if(any(is.na(interim_aux)))next
  interim_aux<-interim_aux+sample_sizes_before75
  interim_ss_rar75<-rbind(interim_ss_rar75,interim_aux)
}
colMeans(interim_ss_rar75)
```

### Scenario 24 no RAR

```{r}
interim_ss_25<-tibble()
df_sample_size<-tibble()
interim_ss_50<-tibble()
df_q_andmu_posteriors_50<-tibble()
df_alpha_beta_posteriors_50<-tibble()
df_D_posteriors_50<-tibble()
interim_allocation_50<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(2/7,1/7,2/7,2/7),q_prior=c(1,1,1,1),delta_star=4.5)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=-1.7, sd=6.9)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=-0.2, sd=6.7)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=-1.4, sd=6.6)
  length4<-round(aux$treatment4/4)
  y4_aux=rnorm(length4,mean=-2.6, sd=7.4)
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D

  
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(2/7,1/7,2/7,2/7),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=4.5)
  if(any(is.na(interim_aux)))next
  interim_aux<-interim_aux+aux/4
  interim_ss_25<-rbind(interim_ss_25,interim_aux)
  

  #Scenario 4
  length1<-max(0,round((interim_aux$treatment1)/2-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=-1.7, sd=6.9)
  length2<-max(0,round((interim_aux$treatment2)/2-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=-0.2, sd=6.7)
  length3<-max(0,round((interim_aux$treatment3)/2-aux$treatment3/4))
  y3_aux=rnorm(length3,mean=-1.4, sd=6.6)
  length4<-max(0,round((interim_aux$treatment4)/2-aux$treatment4/4))
  y4_aux=rnorm(length4,mean=-2.6, sd=7.4)
  
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),rep(3,length3),rep(4,length4))
  df_50=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_50)
  
  aux_post_50<-posterior_calculations(alpha_prior=df_alpha_beta_posteriors_25$alpha_posterior,
                                      beta_prior=df_alpha_beta_posteriors_25$beta_posterior,
                                      q_prior=as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                      mu_prior=as.numeric( df_q_andmu_posteriors_25[,grep("mu",colnames(df_q_andmu_posteriors_25)),]),
                   N_treat = c(round(interim_aux$treatment1/2)+length1,
                                              round(interim_aux$treatment2/2),
                                              round(interim_aux$treatment3/2),
                                              round(interim_aux$treatment4/2)),
                                   y_treatment = df)
  
  sample_sizes_before50<-interim_aux/2
  df_q_andmu_posteriors_50<-aux_post_50$q_andmu_posteriors
  df_alpha_beta_posteriors_50<-aux_post_50$alpha_beta_params
  df_D_posteriors_50<-aux_post_50$D
  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_50$alpha_posterior,beta_prior = df_alpha_beta_posteriors_50$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(2/7,1/7,2/7,2/7),q_prior =as.numeric( df_q_andmu_posteriors_50[,grep("q",colnames(df_q_andmu_posteriors_50)),]),
                                       delta_star=4.5)
    if(any(is.na(interim_aux)))next
  interim_aux<-interim_aux+sample_sizes_before50
   interim_ss_50<-rbind(interim_ss_50,interim_aux)
  
  
}
colMeans(interim_ss_50)
```

### Scenario 25 no RAR

```{r}
interim_ss_25<-tibble()
df_sample_size<-tibble()
interim_ss_75<-tibble()
df_q_andmu_posteriors_75<-tibble()
df_alpha_beta_posteriors_75<-tibble()
df_D_posteriors_75<-tibble()
interim_allocation_75<-tibble()

df_q_andmu_posteriors_25<-tibble()
df_alpha_beta_posteriors_25<-tibble()
df_D_posteriors_25<-tibble()
interim_allocation_25<-tibble()



for(i in 1:length(alpha)){
  aux<-sample_size_calculation(alpha_prior = alpha[i],beta_prior = beta[i], eta=0.95, zeta=0.90, xi=0.95,r=c(2/7,1/7,2/7,2/7),q_prior=c(1,1,1,1),delta_star=4.5)
  if(any(is.na(aux)))next
  df_sample_size<-rbind(df_sample_size,aux)
  #Scenario 4
  length1<-round(aux$treatment1/4)
  y1_aux=rnorm(length1,mean=-1.7, sd=6.9)
  length2<-round(aux$treatment2/4)
  y2_aux=rnorm(length2,mean=-0.2, sd=6.7)
  length3<-round(aux$treatment3/4)
  y3_aux=rnorm(length3,mean=-1.4, sd=6.6)
  length4<-round(aux$treatment4/4)
  y4_aux=rnorm(length4,mean=-2.6, sd=7.4)
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  
  treatment_assignment<-c(rep(1,length1),rep(2,length2),
                          rep(3,length3),rep(4,length4))
  df_25=tibble(treatment_assignment,y)
  
  aux_post_25<-posterior_calculations(alpha_prior=alpha[i],beta_prior=beta[i],q_prior=c(1,1,1,1),mu_prior=c(0,0,0,0),
                                   N_treat = c(length1,length2,length3,length4),
                                   y_treatment = df_25)
  
  df_q_andmu_posteriors_25<-aux_post_25$q_andmu_posteriors
  df_alpha_beta_posteriors_25<-aux_post_25$alpha_beta_params
  df_D_posteriors_25<-aux_post_25$D
  

  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_25$alpha_posterior ,beta_prior = df_alpha_beta_posteriors_25$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(2/7,1/7,2/7,2/7),q_prior =as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                       delta_star=4.5)
  if(any(is.na(interim_aux)))next
  interim_aux<-interim_aux+aux/4
  interim_ss_25<-rbind(interim_ss_25,interim_aux)
  

  #Scenario 5
  length1<-max(0,round((interim_aux$treatment1)*0.75-aux$treatment1/4))
  y1_aux=rnorm(length1,mean=-1.7, sd=6.9)
  length2<-max(0,round((interim_aux$treatment2)*0.75-aux$treatment2/4))
  y2_aux=rnorm(length2,mean=-0.2, sd=6.7)
  length3<-max(0,round((interim_aux$treatment3)*0.75-aux$treatment3/4))
  y3_aux=rnorm(length3,mean=-1.4, sd=6.6)
  length4<-max(0,round((interim_aux$treatment4)*0.75-aux$treatment4/4))
  y4_aux=rnorm(length4,mean=-2.6, sd=7.4)
  y=c(y1_aux,y2_aux,y3_aux,y4_aux)
  treatment_assignment<-c(rep(1,length1),rep(2,length2),rep(3,length3),rep(4,length4))
  df_75=tibble(treatment_assignment,y)
  df<-rbind(df_25,df_75)
  
  aux_post_75<-posterior_calculations(alpha_prior=df_alpha_beta_posteriors_25$alpha_posterior,
                                      beta_prior=df_alpha_beta_posteriors_25$beta_posterior,
                                      q_prior=as.numeric( df_q_andmu_posteriors_25[,grep("q",colnames(df_q_andmu_posteriors_25)),]),
                                      mu_prior=as.numeric( df_q_andmu_posteriors_25[,grep("mu",colnames(df_q_andmu_posteriors_25)),]),
                                      N_treat = c(round(interim_aux$treatment1*0.75),
                                              round(interim_aux$treatment2*3/4),
                                              round(interim_aux$treatment3*3/4),
                                              round(interim_aux$treatment4*3/4)),
                                   y_treatment = df)
  sample_sizes_before75<-interim_aux*0.75
  df_q_andmu_posteriors_75<-aux_post_75$q_andmu_posteriors
  df_alpha_beta_posteriors_75<-aux_post_75$alpha_beta_params
  df_D_posteriors_75<-aux_post_75$D

  interim_aux<-sample_size_calculation(alpha_prior =df_alpha_beta_posteriors_75$alpha_posterior,beta_prior = df_alpha_beta_posteriors_75$beta_posterior, eta=0.95, zeta=0.90, 
                                       xi=0.95,r=c(2/7,1/7,2/7,2/7),q_prior =as.numeric( df_q_andmu_posteriors_75[,grep("q",colnames(df_q_andmu_posteriors_75)),]),
                                       delta_star=4.5)
  if(any(is.na(interim_aux)))next
  interim_aux<-interim_aux+sample_sizes_before75
   interim_ss_75<-rbind(interim_ss_75,interim_aux)
  
  
}
colMeans(interim_ss_75)
```
